### 2018-05-14 manuscript/data.tex
intro, data, related updated

Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of individuals in the city.

@@

While the subset can not fully represent the ground true of society awide, the distribution shows positive sign in even indication. We takes it as a step into the social-spatial dynamics exploration in the context of big social media data. 
% As a note, although it is a subset of all people with

>>>>

Our case-study data is confined to a small proportion of Wechat users who opt to contribute their information and trips.
Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of individuals in the city.

@@

While there is unevitable bias inherent in fully representing the ground true of society awide, the distribution shows positive sign in even indication.

We takes it as a step into the social-spatial dynamics exploration in the context of big social media data and align it with the avaliable of individual characteristics. We believe this work to be one of the nature steps into research of social understanding of the city.
% As a note, although it is a subset of all people with

### 2018-05-14 manuscript/relatedwork.tex
intro, data, related updated

\textbf{Anonymous Movement Analysis} Introduce the classifical movement analysis focus. Data mining (Zheng Yu's work), Specially in the field of visual analytics, also most of work focus on the efficiency of the travel infrustions, (Wang, Lu, Zeng, Qu, Wu Yingcai).

\textbf{Social Related Analysis} In the GIS field, (Liu Yu), Soical Media (Chen, CaoNan)

>>>>

\textbf{Anonymous/Conventional Movement Analysis} Introduce the classifical movement analysis focus. Data mining (Zheng Yu's work), Specially in the field of visual analytics, also most of work focus on the efficiency of the travel infrustions, (Wang, Lu, Zeng, Qu, Wu Yingcai).

\textbf{Social Related Analysis} As the mass adaption of social medial serivces, such as Twitter, Facebook, ti has become an hot research area of ... The new and rich data as Twitter flowerish the research. ... As social media data continues attracting the attention from research fields, such social science, there are lot of research performed around this topics. Most of work infer key characteristics from individuals using social media.

In the GIS field, (Liu Yu), Soical Media (Chen, CaoNan)

\cite{Longley2015}\cite{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.

### 2018-05-14 manuscript/visualdesign.tex
intro, data, related updated

\section{Demographics Driven Map Distortion Method}

\subsection{Data-driven Profile Design}

@@

@@

@@

>>>>

\section{Idea}

Classification method, flow clustering method, Semantic representation.

The key of our work is to align the analysis of urban dynamics with the available of individual characteristics.

Problem to solve: 
\begin{itemize}
\item \textit{Groups of people}: multiple attributes, semantic understanding, loose attribute boundary
\item \textit{Urban Dynamics of People Group}: where those people go and how they access the ... in a city. the patterns of behaviour classified by different social characteristics.  
\end{itemize}

\section{City-folding Visual Analytics}

Semantic understanding of social characteristics.

\subsection{Data-driven Visual Profile}

to abstract to concrete and semantic understanding, to help users clues to do the classification.

Face... Data-driven inforgraphics~\cite{}.

@@

Considering the driven machinsm in two attributes: 
\begin{itemize}
\item \textit{Numerical}
\item \textit{Categorical}
\end{itemize}

@@

Groups from demographics

@@

\subsection{Spatial Visualization}

The space visualization is embedded in 2.5D space. TAZ is used as the .... The height of space is put as the occurrence of visiting. For each group of people, we adjust the DB-Scan Algorithm in the context of TAZ.
